%\thispagestyle{empty}
\newpage
\section*{Acknowledgements}
I want to thank my two supervisors Ms. Gudrun Hiller and Mr. Jean Orloff for good advices and support in solving problems throughout the whole
process. Most of
the training period was spent at the university Blaise Pascal in Clermont-Ferrand, France, which was supported by the ERASMUS+ programme. I want
to thank Vincent Morenás and Ana M. Teixeira and the rest of the staff for the warm reception. I want to thank Mickael Barsive for the nice company 
at the end of my stay and for his
help with the french abstract. Further, I want to thank Christophe Besnier for the nice accommodation during the whole time span. The idea for this 
thesis came during the 2nd BCD International School on High Energy Physics which took place at the institut d'études scientifiques de Cargèse. I thank
the staff and all the participants for this very pleasant week. I want to thank the staff of the T-III and T-IV chair in Dortmund for the good time 
and especially Mathias Becker,
Dennis Loose and Philipp Sicking who took their time to correct make remarks on my work. I have to thank most notably Dominik Kahl and Kai Schönwald 
for very good and fruitful 
discussions. Furthermore, I want to thank my friends Jan Adam, Mario Dunsch, Hannes Franke, Jan Latarius, Florian Schulz and Julius Tilly for the past 
five memorable years and I truly hope that we never lose contact. I want to thank Howard Shore and many other artists for their music accompanying
and inspiring
my entire work. A special thanks goes to my parents and my brothers for the financial and emotional support throughout my whole life. Last but not least
I want to thank my best friend Benjamin Schäfer and my soul mate and life compantion Katharina Goder for the strong support of any kind at any time. 
You are wonderful human beings.



\newpage
\thispagestyle{empty}
\begin{center}
\section*{Eidesstattliche Versicherung}
\end{center}
\begin{spacing}{1,0}
%\vspace*{1cm}
\noindent
Ich versichere hiermit an Eides statt, dass ich die vorliegende Masterarbeit mit dem Titel \glqq{Majorana Dark Matter and its Role in B-anomalies}\grqq \ selbst\"andig und ohne unzulässige fremde Hilfe erbracht habe. Ich habe keine anderen als die angegebenen
Quellen und Hilfsmittel benutzt sowie w\"ortliche und sinngem\"a\ss e Zitate kenntlich gemacht.
Die Arbeit hat in gleicher oder \"ahnlicher Form noch keiner Pr\"ufungsbeh\"orde vorgelegen.
\vspace*{1cm}
\ \\
\ \\
\line(1,0){150} \hfill \line(1,0){150}\\
Ort, Datum \hfill Unterschrift \hspace*{3cm}
\vspace*{1.5cm}

\subsection*{Belehrung}
Wer vorsätzlich gegen eine die T\"auschung über Prüfungsleistungen betreffende Regelung einer Hochschulprüfungsordnung
verstößt handelt ordnungswidrig. Die Ordnungswidrigkeit kann mit einer Geldbu\ss e von bis zu 50.000,00 \euro{} geahndet werden. Zuständige Verwaltungsbehörde für die Verfolgung und Ahndung von Ordnungswidrigkeiten ist
der Kanzler/die Kanzlerin der Technischen Universit\"at Dortmund. Im Falle eines mehrfachen oder sonstigen schwerwiegenden Täuschungsversuches kann der Prüfling zudem exmatrikuliert werden (\S\ 63 Abs. 5 Hochschulgesetz - HG - ).\\
\ \\
Die Abgabe einer falschen Versicherung an Eides statt wird mit Freiheitsstrafe bis zu 3 Jahren oder mit Geldstrafe bestraft.\\
\ \\
Die Technische Universit\"at Dortmund wird ggf. elektronische Vergleichswerkzeuge (wie z.B. die Software ''turnitin'') zur \"Uberpr\"ufung von Ordnungswidrigkeiten in Pr\"ufungsverfahren nutzen.\\
\ \\
Die oben stehende Belehrung habe ich zur Kenntnis genommen.
\vspace*{1cm}
\ \\
\ \\
\line(1,0){150} \hfill \line(1,0){150}\\
Ort, Datum \hfill Unterschrift \hspace*{3cm}
\vspace*{\fill}
\end{spacing}
